Exploring Rural Shrink Smart Through Guided Discovery Dashboards

### 2022-01-17 SCCAbstract_SDSS2022-knitr.tex
App updates

\section{Current Progress}
In our research, it was necessary to use the visual orientation of dashboards and the framework of Guided Discovery Learning (GDL) to make sure that the town analyst can understand the visual orientation easily and guide them to a discovery about possible changes in the dashboard. 
Stephen Few noted in {\it Information Dashboard Design: The effective visual communication of data} stated that visual orientation of dashboards is essential due to the speed at which perception \cite{few}.

@@

A bit of background on Guided Discovery, which is defined as an environment where "students" are actively discovering knowledge, DeDonno states that we use GDL in our daily lives to make decisions by hints, feedback, and helpful information \cite{dedonno}.
%\begin{quotation}
%\small In our daily lives, we may use a guided discovery process where learning is aided by hints, direction, feedback and other helpful information.  \cite{mayer} \cite{dedonno}
%\end{quotation}
Few outlined common mistakes that are made in {\it Information Dashboard Design}, we have focused on making sure that the following three common mistakes on workplace dashboard development are avoided to best assist the town analyst to the best path of success with our solutions to those common mistakes:
\begin{itemize}
\item{ {\bf Choosing inappropriate display media} - Our work has minimized the number of tables and charts that could come from huge open-source data to incorporate highlighted key metrics and visualize data of five towns in parallel coordinate plots.}
\item{ {\bf Ineffectively highlighting what’s important} - We wanted the town to be the center of focus for the user; as such, we added their information in the focal point in the center of the page. The comparison towns are only in the parallel coordinate plots to remind users that their town is the most important item in the dashboard.}
\item{ {\bf Misusing or overusing color} - Our dashboard uses color to highlight the town in the parallel coordinate plot along with the leaflet maps that will be used in the theme of the Rural Shrink Smart Project}
\end{itemize}

The outlined list has been used as the guiding light to avoid pitfalls in developing dashboards in the workplace. With the amount of data, our dashboard could fall into the trap of over ineffectively highlighting what's important and choosing inappropriate display media and misusing color to ensure that the analyst's attention and all of the information is given to the user. This has been a significant hurdle when displaying the amount of data collected from open-source data for the small towns of Iowa.

>>>>

\section{Current Progress}
\svp{We leverage} the framework of Guided Discovery Learning (GDL) to guide \svp{the town leaders} to \svp{make discoveries using our interactive visualization}. \svp{This framework leverages hints, feedback, and other helpful information to guide users in interactive exploration}\cite{dedonno}.
% Stephen Few noted in {\it Information Dashboard Design: The effective visual communication of data} stated that visual orientation of dashboards is essential due to the speed at which perception \cite{few}.

@@

% A bit of background on Guided Discovery, which is defined as an environment where "students" are actively discovering knowledge, DeDonno states that we use GDL in our daily lives to make decisions by hints, feedback, and helpful information .
%\begin{quotation}
%\small In our daily lives, we may use a guided discovery process where learning is aided by hints, direction, feedback and other helpful information.  \cite{mayer} \cite{dedonno}
%\end{quotation}
% Few outlined common mistakes that are made in {\it Information Dashboard Design}, we have focused on making sure that the following three common mistakes on workplace dashboard development are avoided to best assist the town analyst to the best path of success with our solutions to those common mistakes:
% \begin{itemize}
% \item{ {\bf Choosing inappropriate display media} - Our work has minimized the number of tables and charts that could come from huge open-source data to incorporate highlighted key metrics and visualize data of five towns in parallel coordinate plots.}
% \item{ {\bf Ineffectively highlighting what’s important} - We wanted the town to be the center of focus for the user; as such, we added their information in the focal point in the center of the page. The comparison towns are only in the parallel coordinate plots to remind users that their town is the most important item in the dashboard.}
% \item{ {\bf Misusing or overusing color} - Our dashboard uses color to highlight the town in the parallel coordinate plot along with the leaflet maps that will be used in the theme of the Rural Shrink Smart Project}
% \end{itemize}

\svp{We provide users with a town-centric approach: their town is at the center of our application, and comparisons to other, similar towns are secondary. As it can be extremely difficult to predict which towns are optimal for comparison purposes (similar may involve population, region, economic indicators, sports rivalries, and any number of other variables), we allow users to modify a set of suggested comparison towns to indicate other towns of interest.}

\svp{As part of this project, we have assembled a large set of publicly available data (primarily from \url{data.iowa.gov}), but we are careful with how we present this data because it would be easy to overwhelm the user with small details that mask the bigger picture. We select a small subset of towns (out of the 999 towns in Iowa) and a small subset of variables of interest to start with, and then allow the user to increase the complexity of the display in accordance with their interest. This avoids some of the pitfalls of dashboard design that can easily lead to user overload \cite{few}.}

% The outlined list has been used as the guiding light to avoid pitfalls in developing dashboards in the workplace. With the amount of data, our dashboard could fall into the trap of over ineffectively highlighting what's important and choosing inappropriate display media and misusing color to ensure that the analyst's attention and all of the information is given to the user. This has been a significant hurdle when displaying the amount of data collected from open-source data for the small towns of Iowa.
